Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 introduction.tex
fixes

Currently, these concerns need to be addressed \emph{alongside} the
visual analytics environment. Some symptoms of the current situation are:
\begin{itemize}
\item It is hard to find data, metadata, and knowledge about them.
\item Most coordination is done through meetings, whose content is not related to other artifacts and may not even be stored.
\item Production deployment requires porting code to a different environment or even completely rewriting it, thwarting continuous release.
\item Many tools adopt a standalone or single developer perspective,
not suited to collaboration and web deployment. 
\item Analysts find insufficient support for tracing events or issues from production back to the EDA process.
\end{itemize}

In view of the opportunity to improve this situation,
we created a software environment that supports the end to end
visual analytics process for individuals and teams.
This environment knits together some familiar tools, and 
provides new features to find data and code; create experimental workbooks;
run experiments; annotate and deploy experiments as end-user websites or
as reusable, callable services; and to share, search and recommend these artifacts. The artifacts are stored in a version
control system that provides a common workspace, as well as needed control
and isolation between stable and experimental versions of code and other
resources.

>>>>

Currently, these concerns need to be addressed \emph{alongside} the
visual analytics environment. Some symptoms of the current situation are:
\begin{itemize}
\item It is hard to find data, metadata, and knowledge about them.
\item Most coordination is done through meetings, whose content is not linked to other artifacts and may not even be stored.
\item Production deployment requires porting code to a different environment or even completely rewriting it, thwarting continuous release.
\item Many tools adopt a standalone or single developer perspective,
not suited to collaboration and web deployment. 
\item Analysts find insufficient support for tracing events or issues from production back to the EDA process.
\end{itemize}

In view of the opportunity to improve this situation,
we created a software environment that supports the end-to-end
visual analytics process for individuals and teams.
This environment knits together some familiar tools, and 
provides new features to find data and code; create experimental workbooks;
run experiments; annotate and deploy experiments as end-user websites or
as reusable, callable services; and to share, search and recommend these artifacts. The artifacts are stored in a version
control system that provides a common workspace, as well as needed control
and isolation between stable and experimental versions of code and other
resources.
